% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Sha (Lisa) Liu}
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Faculty of Transportation Engineering,Central South University}
 \moveleft.5\hoffset\centerline{CHASHA,HUNAN 410075 China}
 \moveleft.5\hoffset\centerline{(+86)18273133639}

% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\begin{resume}
 
 

\section{EDUCATION} \textbf {CENTRAL SOUTH UNIVERSITY(CSU),China}  \hfill{2016-pres}\\
                    \textbf{ MSc in Transportation Equipment \& Control Engineering} \hfill{GPA:3.4/4.0}\\
                \textbf {\textit {Thesis Focus:}}  3D Reconstruction, Deep Learning ,System Integration \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                {\sl Coursework:} Artificial Neural Network and Its Application, Intelligent detection and signal processing, Vehicle system dynamics, Computational fluid dynamics foundation, Scientific Paper Writing.
                
                \textbf {NANJING AGRICULTURE UNIVERSITY(NAU),China}  \hfill{2012-2016}\\
                    \textbf{ Diploma in Traffic \& Transportation } \hfill{GPA:81.25/100}\\
                \textbf {\textit {Thesis Focus:}}  Smart Transportation\\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                {\sl Coursework:} Intelligent Transportation System, TransCAD, Mechanical Design Basis, Traffic Geographic Information System, Traffic Safety Theory.
 

 
\section{EXPERIENCE} \textbf { CSU, Dept. of Transportation Engineering   } \hfill 2016-pres \\
\textbf {Researcher , CAD/CAM Research Laboratory}
               
                 \begin{itemize}  
                 \itemsep -2pt %reduce space between items
                 \item  Help Scarlett.Liu write Grant "Research on Visual Defect Detection and Recognition based on Deep Learning for EMU's Structural Components 
",Responsibled for writing domestic and foreign research status and innovations, drawing              
                 
                 \hfill 2018.02-03       \item  Participated the grant writing of the project of ''Diversified Technologies for Guided Transport System Models  '' \hfill 2018.01
                \item   Completed the thesis report.
                \item   Completed the Recontruction of  the Railway Park locomotive of CSU.
                \end{itemize}
 
               \textbf { NAU, Dept. of Transportation and Vehicle Engineering   } \hfill 2016.06
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Designed and developed intelligent parking system.
                 \item Learned the TransCAD 
                 \end{itemize} 
               
\section{COURSE \\ INTERSHIP}  \textbf {Mechanical Design - Gear Reducer Courses Design} \hfill{2015.03}
\begin{itemize}  
                 \item \ Designed the second-class gear reducer independently. 
                 \item \ Calculated the various components of Gearbox mechanical and designed the shape. Drawed the parts and assembly drawings, and writed the designing specifications.
                 \end{itemize} 



\section{COMMUNITY \\ SERVICE}  \textbf {Elected as the 2nd ''Youth Olympic Games ''staff}            \hfill{2014.07-08}
                 \newline `` Youth Olympic Games''  an international event organized for young people. Over 200 conturies and 3000 athletes participated . 
  \begin{itemize}  
  \item \ Awarded as Outstanding Member.
   \end{itemize} 
\section{EXTRA-CURRICULAR \\ ACTIVITIES}   
            \textbf { CSU. Graduate Student Union of Faculty of Traffic}  \hfill{2016-2017}  \\\textbf {and Transportation Engineering}     \\  
            {\it Member of Psychological Mutual Aid Team}  
            \begin{itemize}  
                 \item Organized various activities to care about the mental health of graduate students. 
                 \end{itemize} 
                 \begin{itemize}  
                 \item  Awarded as  the third prize of CSU. Psychological Drama Competition. 
                 \end{itemize} 
                 \textbf { CSU. 2016 class 1 of Transportation Equipment }  \hfill{2016-pres}\\
                 \textbf {\& Control Engineering }\\
              {\it Party branch secretary and Arts and sports commissioner} 
              \begin{itemize}  
                 \item  Teacher's assistant,  do a good job in class management and construction work
                 \item Awarded as  CSU. outstanding mission
                 \end{itemize} 
                  \textbf { NAU.Faculty of Transportation and Vehicle Engineering  }  \hfill{2012-2016}\\
                 {\it Member of Young Volunteers Association} \\
                 {\it Member of  Propaganda Department of Student Union} 
             
                
                
\section{ SKILLS }  \textbf {\textit {Computer:}}\\  
 {\sl Engineering:}  \ \ MATLAB, VisualSFM, MeshLab, Python\\ 
 {\sl Programming:} C\\
 {\sl Other:} \ \ \ \ \ \ \ \ \ \ Adobe Photoshop, Latex,  Linux, Win, Office\\
    \textbf {\textit {Language:}} \\ English, Chinese\\
    \textbf {\textit {Activities:}} \\ Badminton, Table Tennis, Singing, Guitar
      
                 
 

\end{resume}
\end{document}




